Select-based random access to variable-byte encodings

### 2020-02-28 gradu/msc_english_contents.tex
Fixes

An alternative solution with $select$ data structure is proposed and explained in detail later. Comparison to $rank$ by Brisaboa et al is shown with different
implementations of $rank$ and $select$ and several different data sets are used. Proposed method does not use data 
reorganizing, but rather capitalizes on the assumption that data is encoded the same way it is in the source. Because variable-byte encoding does not assign 
new codewords to data when encoding, reading the data straight from the memory is much faster than reassembling the word from blocks.

@@

The rank and select implementations used in this article are C++ libraries from \citep{gbmp2014sea}. The library has several implementations of both rank and 
select as well as an implementaion of a bit array. Table~\ref{table:supportsize} has $rank$ and $select$ size requirements of implementations used in this experiment.
Both rank implementations have a constant space requirement, while select's needed size depends on the number of 1's in the data.

@@

$Select$ data structure works similarly to rank. Index location of every 4096th set bit is stored in the superblock and location of every 64th set bit is stored 
relative to the superblock. $Select$

>>>>

An alternative solution with $select$ data structure is proposed and explained in detail later in this thesis. Comparison to $rank$ by Brisaboa et al is shown with different
implementations of $rank$ and $select$ and several different data sets are used. Proposed method does not use data 
reorganizing, but rather capitalizes on the assumption that data is encoded the same way it is in the source. Because variable-byte encoding does not assign 
new codewords to data when encoding, reading the data straight from the memory is much faster than reassembling the word from blocks.

@@

The rank and select implementations used in this article are from C++ library by \citep{gbmp2014sea}. The library has several implementations of both rank and 
select as well as an implementaion of a bit array. Table~\ref{table:supportsize} has $rank$ and $select$ size requirements of implementations used in this experiment.
Both rank implementations have a constant space requirement over the bit array, while select's needed size depends on the number of 1's in the data.

@@

$Select$ data structure works similarly to rank. Index location of every 4096th set bit is stored in the superblock and location of every 64th set bit is stored 
relative to the superblock.
